---
title: "FASTRESS 02 Analysis"
format: 
  # uncomment below to transform into html presentation/document. other options: - powerpoint "pptx:" or - pdf document "pdf:" 
  # revealjs:
  #   slide-number: true
  #   theme: default   # simple, default, dark
  html:
    code-fold: true
    embed-resources: true # makes html self contained, including images etc.
    footer: "Project name"
    number-sections: true
    number-depth: 4
    toc: true
    toc-depth: 3
    toc-expand: 3
    toc-location: left
    toc-title: Contents
editor: visual
---

# Preparation

## Data import

```{r}
#| echo: false
#| warning: false

options(scipen = 999)
parse_num <- function(x) {
  readr::parse_number(stringr::str_replace(as.character(x), ",", "."))
}

library(dplyr)
library(tidyr)
library(stringr)
library(tibble)
library(ggplot2)
library(rstatix)
library(lme4)
library(lmerTest)
library(readr)
library(flextable)  # tables output
library(gtsummary)  # tables
library(broom.mixed)
library(report)

analysis_session <- readRDS("data_clean/analysis_session.rds")
analysis_session_sample <- readRDS("data_clean/analysis_session_sample.rds")
analysis_paired_main <- readRDS("data_clean/analysis_paired_main.rds")
survey_person <- readRDS("data_clean/survey_person.rds")
condition_check <- readRDS("data_clean/condition_check.rds")
stress_person <- readRDS("data_clean/stress_person.rds")
stress_indices_per_session <- readRDS("data_clean/stress_indices_per_session.rds")

blood_person <- readRDS("data_clean/blood_person.rds")
education_person <- readRDS("data_clean/education_person.rds")

# Global options
knitr::opts_chunk$set(echo=FALSE, warning=FALSE, message=FALSE)

# ggplot theme 
s <- 20 # size
sh <- c(21, 2) # shapes
# create theme
theme_main <- theme_classic(base_size = s) + # minimal, gdocs
  theme(
    # panel.grid.major = element_line(),
    legend.position = "bottom",
    strip.background = element_blank(),   # Remove background of facet label area
    strip.text = element_text(face = "bold")  # Customize text appearance
  )
# set theme
ggplot2::theme_set(theme_main)

model_fixed_table <- function(model, digits = 3) {
  broom.mixed::tidy(model, effects = "fixed", conf.int = TRUE) |>
    mutate(across(where(is.numeric), ~ round(.x, digits))) |>
    flextable() |>
    autofit()
}

#rstatistix functions

paired_check <- function(data, col1, col2, label) {
  
  pair_df <- data |>
    transmute(
      a = {{ col1 }},
      b = {{ col2 }}
    ) |>
    tidyr::drop_na()
  
  diff_res <- pair_df |>
    transmute(diff = a - b) |>
    rstatix::shapiro_test(diff) |>
    mutate(
      comparison = label,
      method = "Shapiro-Wilk test of difference score"
    )
  
  long_df <- pair_df |>
    mutate(pair_id = row_number()) |>
    pivot_longer(
      cols = c(a, b),
      names_to = "condition",
      values_to = "value"
    )
  
  t_res <- long_df |>
    rstatix::t_test(value ~ condition, paired = TRUE) |>
    mutate(
      comparison = label,
      method = "Paired t-test"
    )
  
  w_res <- long_df |>
    rstatix::wilcox_test(value ~ condition, paired = TRUE, exact = FALSE) |>
    mutate(
      comparison = label,
      method = "Wilcoxon signed-rank test"
    )
  
  d_res <- long_df |>
    rstatix::cohens_d(value ~ condition, paired = TRUE) |>
    mutate(
      comparison = label,
      method = "Cohen's d"
    )
  
  summary_res <- tibble(
    comparison = label,
    n_pairs = nrow(pair_df),
    shapiro_p = diff_res$p,
    preferred_test = ifelse(diff_res$p > .05, "paired t-test", "wilcoxon signed-rank test")
  )
  
  list(
    summary = summary_res,
    normality = diff_res,
    t_test = t_res,
    wilcox = w_res,
    effect_size = d_res
  )
}

fmt_p <- function(p) {
  ifelse(
    is.na(p), NA_character_,
    ifelse(p < .001, "< .001", sprintf("%.3f", p))
  )
}

paired_result_row <- function(res) {
  
  use_t <- res$summary$preferred_test[1] == "paired t-test"
  
  if (use_t) {
    stat_label <- "t"
    stat_value <- round(res$t_test$statistic[1], 2)
    df_value   <- round(res$t_test$df[1], 2)
    p_value    <- res$t_test$p[1]
  } else {
    stat_label <- "V"
    stat_value <- round(res$wilcox$statistic[1], 2)
    df_value   <- NA_real_
    p_value    <- res$wilcox$p[1]
  }
  
  tibble(
    comparison    = res$summary$comparison[1],
    n_pairs       = res$summary$n_pairs[1],
    shapiro_p     = fmt_p(res$summary$shapiro_p[1]),
    reported_test = res$summary$preferred_test[1],
    statistic     = paste0(stat_label, " = ", stat_value),
    df            = ifelse(is.na(df_value), "", as.character(df_value)),
    p             = fmt_p(p_value),
    cohen_d       = round(res$effect_size$effsize[1], 2),
    magnitude     = res$effect_size$magnitude[1]
  )
}
```

```{r}
#| echo: false
#| warning: false
# ============================================================
# Plot helpers
# ============================================================

plot_theme <- theme_classic(base_size = 16) +
  theme(
    legend.position = "bottom",
    strip.background = element_blank(),
    strip.text = element_text(face = "bold"),
    axis.title = element_text(face = "bold")
  )

cond_labels <- c(
  "satiated" = "Satiated",
  "fasted"   = "Fasted"
)

mean_ci_tbl <- function(data, outcome) {
  data |>
    group_by(planned_condition) |>
    summarise(
      mean = mean(.data[[outcome]], na.rm = TRUE),
      sd = sd(.data[[outcome]], na.rm = TRUE),
      n = sum(!is.na(.data[[outcome]])),
      se = sd / sqrt(n),
      ci_low = mean - 1.96 * se,
      ci_high = mean + 1.96 * se,
      .groups = "drop"
    )
}
```

## Import checks

```{r}
#| include: false
stopifnot("subject" %in% names(analysis_session))
stopifnot(is.factor(analysis_session$subject))
stopifnot("planned_condition" %in% names(analysis_session))

```

# Analysis sample setup

-   `dat_main = fixed main sample from the cleaning script`

-   `ids_complete = exactly those individuals from this main sample`

-   `dat_main_final = the same dataset plus order_group`

## **Main sample**

Create fixed analysis samples

```{r}
# ============================================================
# Analyse Setup: fixes Hauptsample aus dem Cleaning-Skript
# ============================================================

# Main paired within-subject analysis sample
dat_main <- analysis_paired_main

# IDs des finalen Hauptsamples
ids_complete <- dat_main |>
  distinct(fastress_id) |>
  pull(fastress_id)

# QC
dat_main |>
  group_by(fastress_id) |>
  summarise(
    n_rows = n(),
    n_sessions = n_distinct(session),
    n_conditions = n_distinct(planned_condition),
    .groups = "drop"
  ) |>
  count(n_rows, n_sessions, n_conditions) |> flextable()

```

## **Sample overview**

```{r}
# ============================================================
# Sample description: Analyse Samples (Sessions und Personen)
# ============================================================

# Gesamt: alle vorhandenen Sessions mit geplanter Condition
analysis_session |>
  summarise(
    n_total_sessions = sum(!is.na(planned_condition)),
    n_total_persons  = n_distinct(fastress_id[!is.na(planned_condition)])
  )|> flextable()

# Designkonformes Hauptsample: complete cases (2 Sessions pro Person) + Outcome vorhanden
dat_main |>
  summarise(
    n_sessions = n(),
    n_persons  = n_distinct(fastress_id)
  )|> flextable()

# Zusatz: wie viele complete cases wurden identifiziert (Personenebene)
tibble(
  n_complete_persons = length(ids_complete)
)|> flextable()

# Tabelle für Ergebnisteil
dat_main |>
  group_by(planned_condition) |>
  summarise(
    n_sessions = n(),
    n_persons = n_distinct(fastress_id),
    .groups = "drop"
  )|> flextable()

```

# Order and carryover

## Inspect session order structure

Check whether the order of the conditions is relevant:

-   whether participants were fasting or satiated first

-   whether order has a main effect

-   whether order moderates the effect of planned_condition

## Crossover check

```{r}
dat_main |>
  distinct(fastress_id, session, planned_condition) |>
  count(fastress_id) |>
  count(n) |> flextable()

dat_main |>
  count(session, planned_condition)|> flextable()

```

=\> balanced -\> 10 fasted, 10 satiated per session

## Order variable

```{r}
order_tbl <- dat_main |>
  select(fastress_id, session, planned_condition) |>
  mutate(planned_condition = as.character(planned_condition)) |>
  distinct() |>
  pivot_wider(
    names_from = session,
    values_from = planned_condition
  ) |>
  mutate(
    order_group = case_when(
      T1 == "fasted" ~ "fasted_first",
      T1 == "satiated" ~ "satiated_first",
      TRUE ~ NA_character_
    ),
    order_group = factor(order_group, levels = c("satiated_first", "fasted_first"))
  )


order_tbl |> count(order_group)|> flextable()

```

## Merge order

Merge order variable into the main sample

```{r}
dat_main_order <- dat_main |>
  left_join(order_tbl |> select(fastress_id, order_group), by = "fastress_id")

# ============================================================
# QC: Jede Person muss beide Conditions haben
# ============================================================

dat_main_order |>
  group_by(fastress_id) |>
  summarise(
    n_sessions = n_distinct(session),
    n_conditions = n_distinct(planned_condition),
    .groups = "drop"
  ) |>
  count(n_sessions, n_conditions)|> flextable()

# Erwartung: 
# n_sessions = 2 -> Jede Person hat zwei Sessions
# n_condiriona = 2 -> Jede Person hat einmal fasted und einmal satiated

dat_main_order |>
  summarise(
    n_rows = n(),
    n_ids = n_distinct(fastress_id),
    n_missing_order = sum(is.na(order_group))
  )|> flextable()

dat_main_order |> count(order_group, session, planned_condition)|> flextable()

# ============================================================
# Finaler Hauptdatensatz für Hauptanalysen
# ============================================================

dat_main_final <- dat_main_order

# = From now on, the main models will run using dat_main_final, not dat_main.
```

-   `satiated_first`: T1 = satiated, T2 = fasted

-   `fasted_first`: T1 = fasted, T2 = satiated

=\> merge correctly

## Order descriptives

```{r}
dat_main_order |>
  group_by(order_group, planned_condition) |>
  summarise(
    n_obs = n(),
    n_ids = n_distinct(fastress_id),
    total_kcal_M = mean(total_kcal, na.rm = TRUE),
    total_kcal_SD = sd(total_kcal, na.rm = TRUE),
    .groups = "drop"
  )|>
  flextable()

```

## Order models

Test three models:\
A) a baseline model without order;\
B) plus the main effect of order;\
C) plus the interaction between planned_condition and order_group.

-\> If C does not perform better than B, there is no evidence that the condition effect depends on the order.

### Baseline vs. additive order model

```{r}
m_base <- lmer(
  total_kcal ~ planned_condition + (1 | subject),
  data = dat_main_order,
  REML = FALSE
)

m_order_add <- lmer(
  total_kcal ~ planned_condition + order_group + (1 | subject),
  data = dat_main_order,
  REML = FALSE
)

m_order_int <- lmer(
  total_kcal ~ planned_condition * order_group + (1 | subject),
  data = dat_main_order,
  REML = FALSE
)

anova(m_base, m_order_add)

```

**Interpretation**

p = .1644 anova(m_base, m_order_add) is not significant –\> no statistical evidence that the order has an additional main effect on total_kcal.

### Additive order model vs. interaction model

```{r}
anova(m_order_add, m_order_int)


```

### Final order model estimates

```{r}
summary(m_order_int)
confint(m_order_int, method = "Wald")

model_fixed_table(m_order_int)

```

**Interpretation**

p = .1302 anova(m_order_add, m_order_int) is not significant –\> no evidence that order moderates the condition effect

# Sample

## Demographics

Demographic characteristics of the final analysis sample

```{r}
# ============================================================
# Demografie: Analyse-Sample (dat_main_final)
# ============================================================

demo_analysis <- dat_main_final |>
  distinct(fastress_id) |>
  left_join(
    blood_person |>
      select(fastress_id, age, sex_male_m_female_f),
    by = "fastress_id"
  ) |>
  left_join(
    education_person |>
      select(fastress_id, education_label),
    by = "fastress_id"
  )

# # Gesamt N
# N_total <- nrow(demo_analysis)
# 
# # Alter
# age_M   <- mean(demo_analysis$age, na.rm = TRUE)
# age_SD  <- sd(demo_analysis$age, na.rm = TRUE)
# age_min <- min(demo_analysis$age, na.rm = TRUE)
# age_max <- max(demo_analysis$age, na.rm = TRUE)
# 
# # Geschlecht
# gender_tab <- demo_analysis |>
#   count(sex_male_m_female_f) |>
#   mutate(percent = round(n / N_total * 100, 1))
# 
# # Bildung
# edu_tab <- demo_analysis |>
#   count(education) |>
#   mutate(percent = round(n / N_total * 100, 1))
# 
# N_total
# age_M
# age_SD
# age_min
# age_max
# gender_tab
# edu_tab

demo_analysis |> 
  tbl_summary(
    type = list(age ~ "continuous"),
    statistic = list(
      all_continuous() ~ "{mean} ({sd}), [{min}, {max}]",
      all_categorical() ~ "{n} ({p}%)"
    ),
    digits = list(all_continuous() ~ c(2,2,2,2)),
    missing_text = "(missing)", 
    include = -fastress_id  # remove subject from tested variables 
  ) %>%
  bold_labels()
```

# Assumptions

# Manipulation checks

## Stress ratings

```{r}
# ============================================================
# Manipulation check stress: session level, all available data
# ============================================================

stress_check_session <- stress_indices_per_session |>
  filter(
    !is.na(baseline_mean),
    !is.na(mild_mean),
    !is.na(strong_mean)
  )

# QC
stress_check_session |>
  summarise(
    n_obs = n(),
    n_ids = n_distinct(fastress_id),
    n_session_labels = n_distinct(session)
  )

stress_check_session |>
  count(session)|>
  flextable()

# Descriptive statistics
stress_check_session |>
  summarise(
    n_obs = n(),
    n_ids = n_distinct(fastress_id),
    baseline_M = mean(baseline_mean, na.rm = TRUE),
    baseline_SD = sd(baseline_mean, na.rm = TRUE),
    mild_M = mean(mild_mean, na.rm = TRUE),
    mild_SD = sd(mild_mean, na.rm = TRUE),
    strong_M = mean(strong_mean, na.rm = TRUE),
    strong_SD = sd(strong_mean, na.rm = TRUE),
    dMB_M = mean(delta_mild_baseline, na.rm = TRUE),
    dMB_SD = sd(delta_mild_baseline, na.rm = TRUE),
    dSB_M = mean(delta_strong_baseline, na.rm = TRUE),
    dSB_SD = sd(delta_strong_baseline, na.rm = TRUE),
    dSM_M = mean(delta_strong_mild, na.rm = TRUE),
    dSM_SD = sd(delta_strong_mild, na.rm = TRUE),
    peak_M = mean(peak_stress, na.rm = TRUE),
    peak_SD = sd(peak_stress, na.rm = TRUE)
  )|>
  flextable()

```

```{r}
#| include: false

stress_mild_baseline <- paired_check(
  data = stress_check_session,
  col1 = mild_mean,
  col2 = baseline_mean,
  label = "Stress mild - baseline"
)

stress_strong_baseline <- paired_check(
  data = stress_check_session,
  col1 = strong_mean,
  col2 = baseline_mean,
  label = "Stress strong - baseline"
)

stress_strong_mild <- paired_check(
  data = stress_check_session,
  col1 = strong_mean,
  col2 = mild_mean,
  label = "Stress strong - mild"
)
```

### Stress paired test summary

```{r}
bind_rows(
  paired_result_row(stress_mild_baseline),
  paired_result_row(stress_strong_baseline),
  paired_result_row(stress_strong_mild)
) |>
  rename(
    Comparison = comparison,
    `N pairs` = n_pairs,
    `Shapiro p` = shapiro_p,
    `Reported test` = reported_test,
    Statistic = statistic,
    df = df,
    p = p,
    `Cohen's d` = cohen_d,
    Magnitude = magnitude
  ) |>
  flextable() |>
  theme_booktabs() |>
  autofit()
```

```{r}
# ============================================================
# Figure: Stress manipulation check
# ============================================================

stress_plot_df <- stress_check_session |>
  mutate(session_id = paste(fastress_id, session, sep = "_")) |>
  select(session_id, baseline_mean, mild_mean, strong_mean) |>
  pivot_longer(
    cols = c(baseline_mean, mild_mean, strong_mean),
    names_to = "phase",
    values_to = "stress_rating"
  ) |>
  mutate(
    phase = factor(
      phase,
      levels = c("baseline_mean", "mild_mean", "strong_mean"),
      labels = c("Baseline", "Mild stress", "Strong stress")
    )
  )

stress_sum <- stress_plot_df |>
  group_by(phase) |>
  summarise(
    mean = mean(stress_rating, na.rm = TRUE),
    sd = sd(stress_rating, na.rm = TRUE),
    n = sum(!is.na(stress_rating)),
    se = sd / sqrt(n),
    ci_low = mean - 1.96 * se,
    ci_high = mean + 1.96 * se,
    .groups = "drop"
  )

p_stress_check <- ggplot(
  stress_plot_df,
  aes(x = phase, y = stress_rating, group = session_id)
) +
  geom_line(alpha = 0.18) +
  geom_point(alpha = 0.25, size = 1.5) +
  geom_line(
    data = stress_sum,
    aes(x = phase, y = mean, group = 1),
    linewidth = 1.2,
    inherit.aes = FALSE
  ) +
  geom_point(
    data = stress_sum,
    aes(x = phase, y = mean),
    size = 3.5,
    inherit.aes = FALSE
  ) +
  geom_errorbar(
    data = stress_sum,
    aes(x = phase, ymin = ci_low, ymax = ci_high),
    width = 0.08,
    linewidth = 0.8,
    inherit.aes = FALSE
  ) +
  labs(
    title = "Subjective stress ratings across stress phases",
    x = "Stress phase",
    y = "Stress rating"
  ) +
  plot_theme

p_stress_check
```

```{r}

stress_plot_df |>
  ggplot(aes(x = phase, y = stress_rating)) +
  geom_boxplot(width = 0.5, outlier.shape = NA) +
  geom_jitter(width = 0.08, alpha = 0.35) +
  labs(
    title = "Stress ratings across stress phases",
    x = "Stress phase",
    y = "Stress rating"
  ) +
  theme_main
```

According to the Shapiro–Wilk test, the difference values for "mild" vs. "baseline" and "strong" vs. "baseline" did not differ significantly from a normal distribution (p = .124 and p = .082).

For "strong" vs. "mild" the distribution was not met (p = .0167 -\> significant). -\> The corresponding Wilcoxon test was also highly significant.

## Blood markers

```{r}
# ============================================================
# Manipulationcheck Blutmarker: fasted vs satiated (paired)
# ============================================================

blood_wide <- analysis_session |>
  filter(!is.na(planned_condition)) |>
  select(fastress_id, planned_condition, ketones_pre, glucose_pre) |>
  distinct() |>
  pivot_wider(
    names_from = planned_condition,
    values_from = c(ketones_pre, glucose_pre)
  )

# QC
blood_wide |>
  summarise(
    n_persons = n(),
    n_ketones_paired = sum(!is.na(ketones_pre_fasted) & !is.na(ketones_pre_satiated)),
    n_glucose_paired = sum(!is.na(glucose_pre_fasted) & !is.na(glucose_pre_satiated))
  )|>
  flextable()

# Werte robust zu numerisch konvertieren
blood_wide <- blood_wide |>
  mutate(
    across(starts_with("ketones_pre"), parse_num),
across(starts_with("glucose_pre"), parse_num)
  )

```

```{r}
#| include: false

ketones_check <- paired_check(
  data = blood_wide,
  col1 = ketones_pre_fasted,
  col2 = ketones_pre_satiated,
  label = "Ketones fasted - satiated"
)

glucose_check <- paired_check(
  data = blood_wide,
  col1 = glucose_pre_fasted,
  col2 = glucose_pre_satiated,
  label = "Glucose fasted - satiated"
)
```

### Blood marker paired test summary

```{r}
bind_rows(
  paired_result_row(ketones_check),
  paired_result_row(glucose_check)
) |>
  rename(
    Comparison = comparison,
    `N pairs` = n_pairs,
    `Shapiro p` = shapiro_p,
    `Reported test` = reported_test,
    Statistic = statistic,
    df = df,
    p = p,
    `Cohen's d` = cohen_d,
    Magnitude = magnitude
  ) |>
  flextable() |>
  theme_booktabs() |>
  autofit()
```

The metabolic state was more clearly evident in the blood for glucose than for ketones. Although ketone levels were in line with expectations, the evidence is not sufficient in this case. Glucose levels, on the other hand, differed significantly between the conditions.

## Hunger ratings

```{r}
# ============================================================
# Manipulationcheck Hunger: fasted vs satiated (paired)
# ============================================================

hunger_wide <- analysis_session |>
  filter(!is.na(planned_condition), !is.na(hunger_hunger)) |>
  select(fastress_id, planned_condition, hunger_hunger) |>
  distinct() |>
  pivot_wider(
    names_from = planned_condition,
    values_from = hunger_hunger
  )

hunger_wide <- hunger_wide |>
  mutate(
    fasted = parse_num(fasted),
satiated = parse_num(satiated)
  )

# QC
hunger_wide |>
  summarise(
    n_persons = n(),
    n_hunger_paired = sum(!is.na(fasted) & !is.na(satiated))
  )|>
  flextable()

# Deskriptive Werte
hunger_wide |>
  summarise(
    fasted_M = mean(fasted, na.rm = TRUE),
    fasted_SD = sd(fasted, na.rm = TRUE),
    satiated_M = mean(satiated, na.rm = TRUE),
    satiated_SD = sd(satiated, na.rm = TRUE)
  )|>
  flextable()

```

```{r}
#| include: false

hunger_check <- paired_check(
  data = hunger_wide,
  col1 = fasted,
  col2 = satiated,
  label = "Hunger fasted - satiated"
)
```

### Hunger paired test summary

```{r}
paired_result_row(hunger_check) |>
  rename(
    Comparison = comparison,
    `N pairs` = n_pairs,
    `Shapiro p` = shapiro_p,
    `Reported test` = reported_test,
    Statistic = statistic,
    df = df,
    p = p,
    `Cohen's d` = cohen_d,
    Magnitude = magnitude
  ) |>
  flextable() |>
  theme_booktabs() |>
  autofit()
```

```{r}
# ============================================================
# Figure: Manipulation checks for hunger and blood markers
# ============================================================

manip_plot_df <- bind_rows(
  blood_wide |>
    transmute(
      fastress_id,
      measure = "Ketones",
      satiated = ketones_pre_satiated,
      fasted = ketones_pre_fasted
    ),
  blood_wide |>
    transmute(
      fastress_id,
      measure = "Glucose",
      satiated = glucose_pre_satiated,
      fasted = glucose_pre_fasted
    ),
  hunger_wide |>
    transmute(
      fastress_id,
      measure = "Hunger",
      satiated = satiated,
      fasted = fasted
    )
) |>
  pivot_longer(
    cols = c(satiated, fasted),
    names_to = "planned_condition",
    values_to = "value"
  ) |>
  filter(!is.na(value)) |>
  mutate(
    measure = factor(measure, levels = c("Hunger", "Glucose", "Ketones"))
  )

manip_sum <- manip_plot_df |>
  group_by(measure, planned_condition) |>
  summarise(
    mean = mean(value, na.rm = TRUE),
    sd = sd(value, na.rm = TRUE),
    n = sum(!is.na(value)),
    se = sd / sqrt(n),
    ci_low = mean - 1.96 * se,
    ci_high = mean + 1.96 * se,
    .groups = "drop"
  )

p_manip_checks <- ggplot(
  manip_plot_df,
  aes(x = planned_condition, y = value, group = fastress_id)
) +
  geom_line(alpha = 0.25) +
  geom_point(alpha = 0.45, size = 1.8) +
  geom_line(
    data = manip_sum,
    aes(x = planned_condition, y = mean, group = 1),
    linewidth = 1.1,
    inherit.aes = FALSE
  ) +
  geom_point(
    data = manip_sum,
    aes(x = planned_condition, y = mean),
    size = 3.2,
    inherit.aes = FALSE
  ) +
  geom_errorbar(
    data = manip_sum,
    aes(x = planned_condition, ymin = ci_low, ymax = ci_high),
    width = 0.08,
    linewidth = 0.8,
    inherit.aes = FALSE
  ) +
  facet_wrap(~ measure, scales = "free_y") +
  scale_x_discrete(labels = cond_labels) +
  labs(
    title = "Manipulation checks across metabolic conditions",
    x = "Metabolic condition",
    y = "Observed value"
  ) +
  plot_theme

p_manip_checks
```

# Subjective stress reactivity (during MRI)

```{r}
# ============================================================
# MRI-based subjective stress reactivity
# Operationalisation: strong stress minus mild stress
# Person-level mean across available sessions
# ============================================================

mri_reactivity_person <- stress_indices_per_session |>
  filter(!is.na(mild_mean), !is.na(strong_mean)) |>
  transmute(
    fastress_id,
    session,
    mri_reactivity_session = strong_mean - mild_mean
  ) |>
  group_by(fastress_id) |>
  summarise(
    mri_reactivity = mean(mri_reactivity_session, na.rm = TRUE),
    n_sessions_mri = sum(!is.na(mri_reactivity_session)),
    .groups = "drop"
  ) |>
  mutate(
    mri_reactivity_c = as.numeric(
      scale(mri_reactivity, center = TRUE, scale = FALSE)
    )
  )

# Merge into final main dataset
dat_main_final <- dat_main_final |>
  left_join(
    mri_reactivity_person,
    by = "fastress_id"
  )
```

### Association with questionnaire-based SRS

```{r}
dat_main_final |>
  distinct(fastress_id, srs_c, mri_reactivity_c) |>
  summarise(
    r_srs_mri = cor(srs_c, mri_reactivity_c, use = "complete.obs")
  ) |>
  flextable()
```

## Standardized variables for beta coefficients

```{r}
# ============================================================
# Standardisierte Variablen fuer beta (β)
# Fuer β werden Outcome und kontinuierlicher Moderator z-standardisiert
# ============================================================

z_num <- function(x) as.numeric(scale(x))

dat_main_final <- dat_main_final |>
  mutate(
    total_kcal_z = z_num(total_kcal),
    high_kcal_z = z_num(high_kcal),

    srs_z = z_num(srs_c),
    mri_reactivity_z = z_num(mri_reactivity_c),
    sses_z = z_num(sses_c),
    cerq_adaptive_z = z_num(cerq_adaptive_c),
    cerq_maladaptive_z = z_num(cerq_maladaptive_c),
    stadit_z = z_num(stadit_c),
    edeq_restraint_z = z_num(edeq_restraint_c)
  )
```

# Moderator samples

## Moderator-specific datasets

```{r}
# ============================================================
# Moderator spezifische Samples
# ============================================================

dat_main_srs <- dat_main_final |> filter(!is.na(srs_c))
dat_main_mri <- dat_main_final |> filter(!is.na(mri_reactivity_c))
dat_main_sses <- dat_main_final |> filter(!is.na(sses_c))
dat_main_cerq_adaptive <- dat_main_final |> filter(!is.na(cerq_adaptive_c))
dat_main_cerq_maladaptive <- dat_main_final |> filter(!is.na(cerq_maladaptive_c))
dat_main_stadit <- dat_main_final |> filter(!is.na(stadit_c))
dat_main_edeq <- dat_main_final |> filter(!is.na(edeq_restraint_c))

# RQ2 Sample (kommt erst nach Stress Merge, aber Platzhalter ok)
# dat_rq2 wird später erstellt

```

## Moderator N's

Document sample sizes for moderator analyses

```{r}
# ============================================================
# Dokumentation der Ns
# ============================================================

sample_n <- tibble(
  sample = c(
    "dat_main_final",
    "dat_main_srs",
    "dat_main_mri",
    "dat_main_sses",
    "dat_main_cerq_adaptive",
    "dat_main_cerq_maladaptive",
    "dat_main_stadit",
    "dat_main_edeq"
  ),
  n_rows = c(
    nrow(dat_main_final),
    nrow(dat_main_srs),
    nrow(dat_main_mri),
    nrow(dat_main_sses),
    nrow(dat_main_cerq_adaptive),
    nrow(dat_main_cerq_maladaptive),
    nrow(dat_main_stadit),
    nrow(dat_main_edeq)
  ),
  n_ids = c(
    n_distinct(dat_main_final$fastress_id),
    n_distinct(dat_main_srs$fastress_id),
    n_distinct(dat_main_mri$fastress_id),
    n_distinct(dat_main_sses$fastress_id),
    n_distinct(dat_main_cerq_adaptive$fastress_id),
    n_distinct(dat_main_cerq_maladaptive$fastress_id),
    n_distinct(dat_main_stadit$fastress_id),
    n_distinct(dat_main_edeq$fastress_id)
  )
)

sample_n |> flextable()
```

= All moderator-specific analysis datasets are the same size =\> 40 rows and 20 IDs

## Sample flow overview

```{r}
sample_flow_analysis <- tibble(
  sample = c(
    "analysis_session",
    "ids_complete",
    "dat_main",
    "dat_main_final",
    "dat_main_srs",
    "dat_main_mri",
    "dat_main_sses",
    "dat_main_cerq_adaptive",
    "dat_main_cerq_maladaptive",
    "dat_main_stadit",
    "dat_main_edeq"
  ),
  n_rows = c(
    nrow(analysis_session),
    length(ids_complete),
    nrow(dat_main),
    nrow(dat_main_final),
    nrow(dat_main_srs),
    nrow(dat_main_mri),
    nrow(dat_main_sses),
    nrow(dat_main_cerq_adaptive),
    nrow(dat_main_cerq_maladaptive),
    nrow(dat_main_stadit),
    nrow(dat_main_edeq)
  ),
  n_ids = c(
    n_distinct(analysis_session$fastress_id),
    length(ids_complete),
    n_distinct(dat_main$fastress_id),
    n_distinct(dat_main_final$fastress_id),
    n_distinct(dat_main_srs$fastress_id),
    n_distinct(dat_main_mri$fastress_id),
    n_distinct(dat_main_sses$fastress_id),
    n_distinct(dat_main_cerq_adaptive$fastress_id),
    n_distinct(dat_main_cerq_maladaptive$fastress_id),
    n_distinct(dat_main_stadit$fastress_id),
    n_distinct(dat_main_edeq$fastress_id)
  )
)

sample_flow_analysis |> flextable()
```

# Preliminary outcome checks

## Distributions

```{r}
# ============================================================
# Outcome checks (Verteilungen, Nullen, Ausreisser)
# ============================================================

# Outcomes, die du prüfen willst
outcomes <- c("total_kcal", "high_kcal", "low_kcal", "prop_high_kcal")

# 8.1 Anteil Nullen pro Outcome (nur Sessions mit Condition)
dat_main_final |>
  summarise(across(all_of(outcomes), ~mean(.x == 0, na.rm = TRUE), .names = "p_zero_{.col}"))|>
  flextable()

# 8.2 Deskriptive Verteilung (Min, Median, Max, Quantile)
dat_main_final |>
  summarise(across(all_of(outcomes),
                   list(
                     n = ~sum(!is.na(.x)),
                     min = ~min(.x, na.rm = TRUE),
                     p25 = ~quantile(.x, 0.25, na.rm = TRUE),
                     p50 = ~quantile(.x, 0.50, na.rm = TRUE),
                     p75 = ~quantile(.x, 0.75, na.rm = TRUE),
                     p95 = ~quantile(.x, 0.95, na.rm = TRUE),
                     max = ~max(.x, na.rm = TRUE)
                   ),
                   .names = "{.col}_{.fn}"))|>
  flextable()

# 8.3 Top Ausreisser Sessions anschauen (nach total_kcal)
dat_main_final |>
  arrange(desc(total_kcal)) |>
  select(fastress_id, session, planned_condition, total_kcal, high_kcal, low_kcal, prop_high_kcal) |>
  slice_head(n = 10)|>
  flextable()

# 8.4 Quick Plots
p_hist_kcal <- dat_main_final |>
  ggplot(aes(x = total_kcal)) +
  geom_histogram(bins = 20) +
  facet_wrap(~planned_condition) +
  labs(title = "total_kcal Verteilung nach Condition")
p_hist_kcal
ggsave("figures/figure_hist_kcal.png", plot = p_hist_kcal, width = 8, height = 5, dpi = 300, bg = "white")

p_boxplot_kcal <- dat_main_final |>
  ggplot(aes(x = planned_condition, y = total_kcal)) +
  geom_boxplot() +
  stat_summary(fun = mean, geom = "point", size = 3) +
  stat_summary(fun = mean, geom = "crossbar", width = 0.4, linewidth = 0.5) +
  labs(title = "Total kcal by metabolic condition", x = "Metabolic condition", y = "Total kcal") +
  theme_main
p_boxplot_kcal
ggsave("figures/figure_boxplot_kcal.png", plot = p_boxplot_kcal, width = 6, height = 5, dpi = 300, bg = "white")

# ============================================================
# Trait distributions (centered)
# ============================================================
p_trait_dist_c <- dat_main_final |>
  select(fastress_id, srs_c, stadit_c, cerq_adaptive_c,
         cerq_maladaptive_c, edeq_restraint_c, sses_c) |>
  distinct() |>
  pivot_longer(-fastress_id) |>
  ggplot(aes(x = value)) +
  geom_histogram(bins = 10) +
  facet_wrap(~ name, scales = "free_x", ncol = 2) +
  labs(title = "Distribution of trait moderators (mean-centred)", x = "Value (mean-centred)", y = "Count") +
  plot_theme
p_trait_dist_c
ggsave("figures/figure_trait_dist_centered.png", plot = p_trait_dist_c, width = 8, height = 10, dpi = 300, bg = "white")

# ============================================================
# Trait distributions (raw)
# ============================================================
p_trait_dist_raw <- dat_main_final |>
  select(fastress_id, srs_mean, stadit_trait_anxiety, cerq_adaptive_mean,
         cerq_maladaptive_mean, edeq_restraint, sses_mean) |>
  distinct() |>
  pivot_longer(-fastress_id) |>
  mutate(name = recode(name,
    "srs_mean"              = "Stress reactivity (SRS)",
    "stadit_trait_anxiety"  = "Trait anxiety (STADI)",
    "cerq_adaptive_mean"    = "Adaptive ER (CERQ)",
    "cerq_maladaptive_mean" = "Maladaptive ER (CERQ)",
    "edeq_restraint"        = "Restrained eating (EDE-Q)",
    "sses_mean"             = "Stress-induced eating (SSES)"
  )) |>
  ggplot(aes(x = value)) +
  geom_histogram(bins = 10, fill = "grey60", color = "white") +
  facet_wrap(~ name, scales = "free_x", ncol = 2) +
  labs(title = "Distribution of trait moderators (raw scores)", x = "Raw score", y = "Count") +
  plot_theme
p_trait_dist_raw
ggsave("figures/figure_trait_dist_raw.png", plot = p_trait_dist_raw, width = 8, height = 10, dpi = 300, bg = "white")
```

## Descriptives

```{r}
# --------------------------------------------------
# Descriptives by planned condition
# --------------------------------------------------

#Alle Sessions: explorativer Überblick (nicht für Hypothesentests)
analysis_session |>
  filter(!is.na(planned_condition)) |>
  group_by(planned_condition) |>
  summarise(
    n_obs = n(),
    n_ids = n_distinct(fastress_id),
    total_kcal_M = mean(total_kcal, na.rm = TRUE),
    total_kcal_SD = sd(total_kcal, na.rm = TRUE),
    high_kcal_M = mean(high_kcal, na.rm = TRUE),
    high_kcal_SD = sd(high_kcal, na.rm = TRUE),
    low_kcal_M = mean(low_kcal, na.rm = TRUE),
    low_kcal_SD = sd(low_kcal, na.rm = TRUE),
    prop_high_M = mean(prop_high_kcal, na.rm = TRUE),
    prop_high_SD = sd(prop_high_kcal, na.rm = TRUE),
    .groups = "drop"
  ) |> 
  flextable()


# Haupttabelle: nur für complete cases des finalen Hauptsamples
dat_main_final |>
  group_by(planned_condition) |>
  summarise(
    n_obs = n(),
    n_ids = n_distinct(fastress_id),
    total_kcal_M = mean(total_kcal, na.rm = TRUE),
    total_kcal_SD = sd(total_kcal, na.rm = TRUE),
    .groups = "drop"
  ) |>
  flextable()

dat_main_final |>
  group_by(planned_condition) |>
  summarise(
    high_kcal_M = mean(high_kcal),
    high_kcal_SD = sd(high_kcal),
    low_kcal_M = mean(low_kcal),
    low_kcal_SD = sd(low_kcal),
    prop_M = mean(prop_high_kcal),
    prop_SD = sd(prop_high_kcal)
  )|>
  flextable()
```

# Model specification

## Random effects

First, use a random intercept as the main model

Then test the random slope

-   Only include the random slope if the model is stable

-   no major warnings appear

-   and the fit is visibly better

=\> A random-intercept model was retained as the primary specification, as adding a random slope for planned_condition was not considered sufficiently justified given the small sample and two observations per subject.

```{r}

# wenn N genügend gross, prüfen -> sonst weglassen

# ============================================================
# Modellstruktur prüfen: Random Intercept versus Random Slope
# ============================================================

# Vor der finalen Hauptanalyse aktivieren

# m_ri <- lmer(
#   total_kcal ~ planned_condition + (1 | subject),
#   data = dat_main_final,
#   REML = FALSE
# )

# m_rs <- lmer(
#   total_kcal ~ planned_condition + (1 + planned_condition || subject),
#   data = dat_main_final,
#   REML = FALSE
# )

# anova_ri_rs <- anova(m_ri, m_rs)
# print(anova_ri_rs)

# summary(m_rs)
# isSingular(m_rs, tol = 1e-4)

use_random_slope <- FALSE

```

## Model helpers

Define reporting functions for mixed models

```{r}
# ============================================================
# Funktionen: report ready Output fuer Mixed Models
# ============================================================

fit_main_effect <- function(dat, outcome, use_random_slope = FALSE) {

  if (use_random_slope) {
    f_m1 <- as.formula(
      paste0(outcome, " ~ planned_condition + (1 + planned_condition || subject)")
    )
  } else {
    f_m1 <- as.formula(
      paste0(outcome, " ~ planned_condition + (1 | subject)")
    )
  }

  f_m0 <- as.formula(
    paste0(outcome, " ~ 1 + (1 | subject)")
  )

  m1 <- lmer(f_m1, data = dat, REML = FALSE)
  m0 <- lmer(f_m0, data = dat, REML = FALSE)

  list(m0 = m0, m1 = m1)
}

model_summary_pack <- function(m0, m1, dat, outcome) {

  comp <- anova(m0, m1)
  ci <- confint(m1, method = "Wald")

  beta <- fixef(m1)
  beta_cond <- beta[grep("^planned_condition", names(beta))][1]

  sd_y <- dat |>
    summarise(sd_y = sd(.data[[outcome]], na.rm = TRUE)) |>
    pull(sd_y)

  eff_sd <- beta_cond / sd_y

  list(
    comparison = comp,
    fixed = summary(m1)$coefficients,
    ci = ci,
    eff_sd = eff_sd
  )
}

```

# Main analyses

## Condition effects

```{r}
# # ============================================================
# # Hauptanalyse: Condition Effekt für alle Outcomes
# # ============================================================
# 
# results_main <- list()
# 
# # ------------------------------------------------------------
# # Outcome: total_kcal => RQ1, H1
# # ------------------------------------------------------------
# m0_total <- lmer(total_kcal ~ order_group + (1 | subject), data = dat_main_final, REML = FALSE)
# m1_total <- lmer(total_kcal ~ planned_condition + order_group + (1 | subject), data = dat_main_final, REML = FALSE)
# 
# anova(m0_total, m1_total) |> 
#   as.data.frame() |> 
#   flextable()
# 
# results_main[["total_kcal"]] <- list(m0 = m0_total, m1 = m1_total) 
# 
# # ------------------------------------------------------------
# # Outcome: high_kcal
# # ------------------------------------------------------------
# m0_high <- lmer(high_kcal ~ order_group + (1 | subject), data = dat_main_final, REML = FALSE)
# m1_high <- lmer(high_kcal ~ planned_condition + order_group + (1 | subject), data = dat_main_final, REML = FALSE)
# 
# anova(m0_high, m1_high) |> as.data.frame() |> 
#   flextable()
# #summary(m1_high)
# #confint(m1_high, method = "Wald")
# 
# results_main[["high_kcal"]] <- list(m0 = m0_high, m1 = m1_high)
# 
# # ------------------------------------------------------------
# # Outcome: low_kcal
# # ------------------------------------------------------------
# m0_low <- lmer(low_kcal ~ order_group + (1 | subject), data = dat_main_final, REML = FALSE)
# m1_low <- lmer(low_kcal ~ planned_condition + order_group + (1 | subject), data = dat_main_final, REML = FALSE)
# 
# anova(m0_low, m1_low) |> as.data.frame() |> 
#   flextable()
# #summary(m1_low)
# #confint(m1_low, method = "Wald")
# 
# results_main[["low_kcal"]] <- list(m0 = m0_low, m1 = m1_low)
# 
# # ------------------------------------------------------------
# # Outcome: prop_high_kcal
# # ------------------------------------------------------------
# m0_prop <- lmer(prop_high_kcal ~ order_group + (1 | subject), data = dat_main_final, REML = FALSE)
# m1_prop <- lmer(prop_high_kcal ~ planned_condition + order_group + (1 | subject), data = dat_main_final, REML = FALSE)
# 
# 
# anova(m0_prop, m1_prop) |> as.data.frame() |> 
#   flextable()
# #summary(m1_prop)
# #confint(m1_prop, method = "Wald")
# 
# results_main[["prop_high_kcal"]] <- list(m0 = m0_prop, m1 = m1_prop)



```

### Summary across all outcomes

```{r}
# ============================================================
# Hauptanalyse: Condition Effekt für alle Outcomes
# kompakte Übersichtstabelle
# ============================================================

extract_main_row <- function(pack, outcome_label) {
  fixed <- as.data.frame(pack$fixed) |>
    tibble::rownames_to_column("term")

  ci <- as.data.frame(pack$ci) |>
    tibble::rownames_to_column("term")

  cond_row <- fixed |>
    filter(term == "planned_conditionfasted")

  cond_ci <- ci |>
    filter(term == "planned_conditionfasted")

  tibble(
    outcome = outcome_label,
    estimate = cond_row$Estimate,
    se = cond_row$`Std. Error`,       
    conf_low = cond_ci$`2.5 %`,
    conf_high = cond_ci$`97.5 %`,
    chisq = pack$comparison$Chisq[2],
    df = pack$comparison$Df[2],
    p_model = pack$comparison$`Pr(>Chisq)`[2]
  )
}

# Modelle fitten
fit_total <- fit_main_effect(dat_main_final, "total_kcal", use_random_slope)
fit_high  <- fit_main_effect(dat_main_final, "high_kcal", use_random_slope)
fit_low   <- fit_main_effect(dat_main_final, "low_kcal", use_random_slope)
fit_prop  <- fit_main_effect(dat_main_final, "prop_high_kcal", use_random_slope)

# Ergebnisse speichern
results_main <- list(
  total_kcal = fit_total,
  high_kcal = fit_high,
  low_kcal = fit_low,
  prop_high_kcal = fit_prop
)

# Reporting-Pakete erzeugen
pack_total <- model_summary_pack(fit_total$m0, fit_total$m1, dat_main_final, "total_kcal")
pack_high  <- model_summary_pack(fit_high$m0,  fit_high$m1,  dat_main_final, "high_kcal")
pack_low   <- model_summary_pack(fit_low$m0,   fit_low$m1,   dat_main_final, "low_kcal")
pack_prop  <- model_summary_pack(fit_prop$m0,  fit_prop$m1,  dat_main_final, "prop_high_kcal")


# Kompakte Ergebnistabelle
tbl_main_results <- bind_rows(
  extract_main_row(pack_total, "Total kcal"),
  extract_main_row(pack_high,  "High-kcal foods"),
  extract_main_row(pack_low,   "Low-kcal foods"),
  extract_main_row(pack_prop,  "Proportion high-kcal")
) |>
  mutate(
    estimate = round(estimate, 2),
     se = round(se, 2),
    conf_int = sprintf("[%.2f, %.2f]", conf_low, conf_high),
    chisq = round(chisq, 2),
    p_model = ifelse(p_model < .001, "< .001", sprintf("%.3f", p_model))
  ) |>
  select(outcome, estimate, se, conf_int, chisq, df, p_model) |>
  rename(
    Outcome = outcome,
    `b (fasted)` = estimate,
    `SE` = se, 
    `95% CI` = conf_int,
    `χ²` = chisq,
    `df` = df,
    `p` = p_model
  )

tbl_main_results |>
  flextable() |>
  theme_booktabs() |>
  autofit()
```

```{r}
# ============================================================
# Figure: Forest plot for main effects
# ============================================================

extract_condition_effect <- function(model, outcome_label) {
  coef_df <- as.data.frame(summary(model)$coefficients) |>
    tibble::rownames_to_column("term")

  ci_df <- as.data.frame(confint(model, method = "Wald")) |>
    tibble::rownames_to_column("term")

  coef_df |>
    filter(term == "planned_conditionfasted") |>
    left_join(ci_df, by = "term") |>
    transmute(
      outcome = outcome_label,
      estimate = Estimate,
      conf_low = `2.5 %`,
      conf_high = `97.5 %`
    )
}

forest_main <- bind_rows(
  extract_condition_effect(results_main[["total_kcal"]]$m1, "Total kcal"),
  extract_condition_effect(results_main[["high_kcal"]]$m1, "High-kcal foods"),
  extract_condition_effect(results_main[["low_kcal"]]$m1, "Low-kcal foods"),
  extract_condition_effect(results_main[["prop_high_kcal"]]$m1, "Proportion high-kcal")
) |>
  mutate(
    outcome = factor(
      outcome,
      levels = rev(c("Total kcal", "High-kcal foods", "Low-kcal foods", "Proportion high-kcal"))
    )
  )

p_forest_main <- ggplot(forest_main, aes(x = estimate, y = outcome)) +
  geom_vline(xintercept = 0, linetype = 2) +
  geom_segment(
    aes(x = conf_low, xend = conf_high, y = outcome, yend = outcome),
    linewidth = 0.8
  ) +
  geom_point(size = 3) +
  labs(
    title = "Estimated effect of fasting across outcomes",
    x = "Estimate for fasted vs. satiated",
    y = NULL
  ) +
  plot_theme

p_forest_main
```

## Session Effects

```{r}
# # ============================================================
# # Sensitivität: Periodeneffekt von session (T1 vs T2)
# # ============================================================
# 
# m_period0 <- lmer(
#   total_kcal ~ planned_condition + order_group + (1 | subject),
#   data = dat_main_final,
#   REML = FALSE
# )
# 
# m_period1 <- lmer(
#   total_kcal ~ planned_condition + session + order_group + (1 | subject),
#   data = dat_main_final,
#   REML = FALSE
# )
# 
# anova(m_period0, m_period1)
# summary(m_period1)
# confint(m_period1, method = "Wald")


```

### Fixed effects including session

```{r}
# ============================================================
# Session effect: kompakte Ergebnistabelle
# ============================================================

m_period0 <- lmer(
  total_kcal ~ planned_condition + (1 | subject),
  data = dat_main_final,
  REML = FALSE
)

m_period1 <- lmer(
  total_kcal ~ planned_condition + session + (1 | subject),
  data = dat_main_final,
  REML = FALSE
)

comp_period <- anova(m_period0, m_period1)

coef_period <- as.data.frame(summary(m_period1)$coefficients) |>
  tibble::rownames_to_column("term")

ci_period <- as.data.frame(confint(m_period1, method = "Wald")) |>
  tibble::rownames_to_column("term") |>
  filter(!term %in% c(".sig01", ".sigma"))

tbl_period <- coef_period |>
  left_join(ci_period, by = "term") |>
  filter(term %in% c("planned_conditionfasted", "sessionT2")) |>
  mutate(
    Effect = c("Fasted vs. satiated", "T2 vs. T1"),
    Estimate = round(Estimate, 2),
    CI = sprintf("[%.2f, %.2f]", `2.5 %`, `97.5 %`),
    p = ifelse(`Pr(>|t|)` < .001, "< .001", sprintf("%.3f", `Pr(>|t|)`))
  ) |>
  select(Effect, Estimate, CI, p)

tbl_period |>
  flextable() |>
  theme_booktabs() |>
  bold(part = "header") |>
  autofit()

```

### Model comparison for adding session

```{r}
# Modellvergleich 
tibble(
  Comparison = "Adding session",
  Chisq = round(comp_period$Chisq[2], 2),
  df = comp_period$Df[2],
  p = sprintf("%.3f", comp_period$`Pr(>Chisq)`[2])
) |>
  flextable() |>
  theme_booktabs() |>
  bold(part = "header") |>
  autofit()
```

# Moderation analyses

## Moderation helper functions

```{r}
# ============================================================
# Moderationen Schritt für Schritt: total_kcal
# ============================================================
# ------------------------------------------------------------
# Mini QC Function: How many complete cases are there in a moderated sample?
# ------------------------------------------------------------
qc_mod_sample <- function(dat, outcome, cond = "planned_condition", mod) {
  dat |>
    summarise(
      n_rows = n(),
      n_ids = n_distinct(fastress_id),
      n_nonmiss_outcome = sum(!is.na(.data[[outcome]])),
      n_nonmiss_cond = sum(!is.na(.data[[cond]])),
      n_nonmiss_mod = sum(!is.na(.data[[mod]])),
      n_complete_for_model = sum(!is.na(.data[[outcome]]) & !is.na(.data[[cond]]) & !is.na(.data[[mod]]))
    )
}

# --------------------------------------------------
# Guard: stop if no complete cases for the moderation model
# --------------------------------------------------
stop_if_no_cases <- function(qc_tbl) {
  n_cc <- qc_tbl$n_complete_for_model[1]
  if (is.na(n_cc) || n_cc == 0) {
    stop("Keine vollstaendigen Faelle fuer dieses Moderationsmodell. Sample ist leer oder hat NAs.")
  }
}

get_interaction_term <- function(model, moderator_name) {
  term_names <- names(fixef(model))

  hit <- term_names[
    stringr::str_detect(
      term_names,
      paste0("^planned_condition.*:", moderator_name, "$|^", moderator_name, ":planned_condition")
    )
  ]

  if (length(hit) != 1) {
    stop("Interaktionsterm konnte nicht eindeutig identifiziert werden.")
  }

  hit
}

fit_moderation <- function(dat, outcome, moderator,
                           outcome_z = paste0(outcome, "_z"),
                           moderator_z = sub("_c$", "_z", moderator)) {

  qc_tbl <- qc_mod_sample(dat, outcome = outcome, mod = moderator)
  stop_if_no_cases(qc_tbl)

  # Raw Modelle
  f_add <- as.formula(
    paste0(outcome, " ~ planned_condition + ", moderator, " + (1 | subject)")
  )

  f_int <- as.formula(
    paste0(outcome, " ~ planned_condition * ", moderator, " + (1 | subject)")
  )

  m_add <- lmer(f_add, data = dat, REML = FALSE)
  m_int <- lmer(f_int, data = dat, REML = FALSE)

  # Standardisiertes Interaktionsmodell fuer beta (β)
  f_int_std <- as.formula(
    paste0(outcome_z, " ~ planned_condition * ", moderator_z, " + (1 | subject)")
  )

  m_int_std <- lmer(f_int_std, data = dat, REML = FALSE)

  int_term_raw <- get_interaction_term(m_int, moderator)
  int_term_std <- get_interaction_term(m_int_std, moderator_z)

  list(
    qc = qc_tbl,
    add = m_add,
    int = m_int,
    int_std = m_int_std,
    anova = anova(m_add, m_int),
    fixed = summary(m_int)$coefficients,
    ci = confint(m_int, method = "Wald"),
    int_term_raw = int_term_raw,
    int_term_std = int_term_std,
    beta_std = fixef(m_int_std)[int_term_std]
  )
}

extract_moderation_interaction_row <- function(res, moderator_label) {

  fixed <- as.data.frame(res$fixed) |>
    tibble::rownames_to_column("term")

  ci <- as.data.frame(res$ci) |>
    tibble::rownames_to_column("term")

  row_raw <- fixed |>
    filter(term == res$int_term_raw)

  row_ci <- ci |>
    filter(term == res$int_term_raw)

  tibble(
    Moderator = moderator_label,
    b = round(row_raw$Estimate, 2),
    beta = round(unname(res$beta_std), 2),
    conf_int = sprintf("[%.2f, %.2f]", row_ci$`2.5 %`, row_ci$`97.5 %`),
    p = ifelse(row_raw$`Pr(>|t|)` < .001, "< .001", sprintf("%.3f", row_raw$`Pr(>|t|)`))
  )
}

```

### Moderation 1: SRS

m_srs_add = main effect of Condition plus main effect of Moderator

m_srs_int = plus interaction; ANOVA tests whether the interaction provides additional explanatory power

#### Sample check

```{r}
# ------------------------------------------------------------
# Moderation 1: SRS (srs_c)
# Outcome: total_kcal
# Sample: dat_main_srs
# RQ2: H2
# ------------------------------------------------------------

srs_res <- fit_moderation(
  dat = dat_main_srs,
  outcome = "total_kcal",
  moderator = "srs_c"
)

srs_res$qc |> flextable()


```

#### Model comparison

```{r}
as.data.frame(srs_res$anova) |> flextable()

```

m_srs_add -\> The interaction model does not fit significantly better than the additive model.

#### Interaction model estimates

```{r}
model_fixed_table(srs_res$int)
```

## Additional Analysis: MRI subjective stress reactivity

```{r}
# ------------------------------------------------------------
# MRI-based subjective stress reactivity (mri_reactivity_c)
# Outcome: total_kcal
# Sample: dat_main_mri
# Additional analysis
# ------------------------------------------------------------

mri_res <- fit_moderation(
  dat = dat_main_mri,
  outcome = "total_kcal",
  moderator = "mri_reactivity_c"
)

mri_res$qc |> flextable()
as.data.frame(mri_res$anova) |> flextable()
model_fixed_table(mri_res$int)


```

### Moderation 2: CERQ

#### Adaptive CERQ

```{r}
# ------------------------------------------------------------
# Moderation 2: CERQ (cerq_c)
# Outcome: total_kcal
# Sample: dat_main_cerq_adaptive
#         dat_main_cerq_maladaptive
# ------------------------------------------------------------

# CERQ adaptive
cerq_adapt_res <- fit_moderation(
  dat = dat_main_cerq_adaptive,
  outcome = "total_kcal",
  moderator = "cerq_adaptive_c"
)

cerq_adapt_res$qc |> flextable()

```

#### Model comparison

```{r}
as.data.frame(cerq_adapt_res$anova) |> flextable()

```

m_cerq_adapt_add -\> There is no evidence that adaptive CERQ moderates the condition effect.

#### Interaction model estimates

```{r}
model_fixed_table(cerq_adapt_res$int)


```

#### Maladaptive CERQ

```{r}

# CERQ maladaptive
cerq_mal_res <- fit_moderation(
  dat = dat_main_cerq_maladaptive,
  outcome = "total_kcal",
  moderator = "cerq_maladaptive_c"
)

cerq_mal_res$qc |> flextable()

```

#### Model comparison

```{r}
as.data.frame(cerq_mal_res$anova) |> flextable()

```

#### Interaction model estimates

```{r}
model_fixed_table(cerq_mal_res$int)

```

H3a was not supported: there was no evidence that adaptive cognitive emotion regulation moderated the association between metabolic condition and total caloric intake. -\> direction was even positive

H3b was not supported: maladaptive cognitive emotion regulation was not significantly associated with greater caloric intake, and no significant interaction with metabolic condition was observed. -\> direction was even negative

### Moderation 3: STADI Trait Anxiety

#### Total caloric intake

```{r}
# ------------------------------------------------------------
# Moderation 3: STADI Trait Anxiety (stadit_c)
# Outcome: total_kcal & high_kcal
# Sample: dat_main_stadit
# ------------------------------------------------------------

# total_kcal
stadit_res <- fit_moderation(
  dat = dat_main_stadit,
  outcome = "total_kcal",
  moderator = "stadit_c"
)

stadit_res$qc |> flextable()

```

#### Model comparison

```{r}
as.data.frame(stadit_res$anova) |> flextable()

```

m_stadit_add -\> The interaction model does not fit significantly better than the additive model. = There is no evidence that trait anxiety moderates the effect of metabolic condition on total_kcal.

#### Interaction model estimates

```{r}
model_fixed_table(stadit_res$int)
```

#### High-calorie intake

```{r}
# high_kcal
stadit_high_res <- fit_moderation(
  dat = dat_main_stadit,
  outcome = "high_kcal",
  moderator = "stadit_c"
)


```

#### Model comparison

```{r}
as.data.frame(stadit_high_res$anova) |> flextable()
```

#### Interaction model estimates

```{r}
model_fixed_table(stadit_high_res$int)

```

**H4a was not supported:** trait anxiety was not significantly associated with total caloric intake or high-calorie intake.

**H4b was not supported:** there was no evidence that trait anxiety moderated the effect of metabolic condition on either total caloric intake or high-calorie intake.

### Moderation 4: EDEQ & SSES

### EDE-Q restraint

```{r}
# ------------------------------------------------------------
# Moderation 4: EDEQ Restraint (edeq_restraint_c)
# Outcome: total_kcal
# Sample: dat_main_edeq
# H5: 
# ------------------------------------------------------------

edeq_res <- fit_moderation(
  dat = dat_main_edeq,
  outcome = "total_kcal",
  moderator = "edeq_restraint_c"
)

edeq_res$qc |> flextable()

```

#### Model comparison

```{r}
as.data.frame(edeq_res$anova) |> flextable()
```

#### Interaction model estimates

```{r}
model_fixed_table(edeq_res$int)

```

### SSES

```{r}
# ------------------------------------------------------------
# H5b: Stress Eating (SSES)
# Outcome: total_kcal
# Sample: dat_main_sses
# ------------------------------------------------------------

sses_res <- fit_moderation(
  dat = dat_main_sses,
  outcome = "total_kcal",
  moderator = "sses_c"
)

sses_res$qc |> flextable()

```

#### Model comparison

```{r}
as.data.frame(sses_res$anova) |> flextable()
```

m_edeq_add -\> The interaction model does not fit significantly better than the additive model = There is no evidence that restrained eating moderates the effect of metabolic condition on total_kcal.

#### Interaction model estimates

```{r}
model_fixed_table(sses_res$int)
```

H5 was not supported for restrained eating: EDE-Q restraint was neither significantly associated with total caloric intake nor did it significantly moderate the effect of metabolic condition.\
-\> but: With increasing restraint in eating, the difference between fasted and satiated states becomes slightly more positive in numerical terms.

H5 was also not supported for stress eating tendencies: SSES showed neither a significant main effect on total caloric intake nor a significant interaction with metabolic condition.

## Overview all Moderations

```{r}
tbl_moderation <- bind_rows(
  extract_moderation_interaction_row(srs_res,        "Stress reactivity (SRS)"),
  extract_moderation_interaction_row(mri_res,        "Stress reactivity (MRI-task)"),
  extract_moderation_interaction_row(cerq_adapt_res, "Adaptive ER (CERQ)"),
  extract_moderation_interaction_row(cerq_mal_res,   "Maladaptive ER (CERQ)"),
  extract_moderation_interaction_row(stadit_res,     "Trait anxiety (STADI)"),
  extract_moderation_interaction_row(edeq_res,       "Restrained eating (EDE-Q)"),
  extract_moderation_interaction_row(sses_res,       "Stress-induced eating (SSES)")
) |>
  rename(
    Moderator = Moderator,
    `b` = b,
    `β` = beta,
    `95% CI` = conf_int,
    `p` = p
  )

tbl_moderation |>
  flextable() |>
  theme_booktabs() |>
  autofit()
```

## Store models

```{r}
# ============================================================
# Moderationsmodelle speichern
# ============================================================

results_mod_total <- list(
  srs = list(add = srs_res$add, int = srs_res$int),
  mri = list(add = mri_res$add, int = mri_res$int),
  sses = list(add = sses_res$add, int = sses_res$int),
  cerq_adapt = list(add = cerq_adapt_res$add, int = cerq_adapt_res$int),
  cerq_mal   = list(add = cerq_mal_res$add, int = cerq_mal_res$int),
  stadit = list(add = stadit_res$add, int = stadit_res$int),
  edeq   = list(add = edeq_res$add, int = edeq_res$int)
)

```

## Moderation summary

This table summarises whether the interaction model improved model fit over the additive model for each moderator.

```{r}
# ============================================================
# Tabelle: Moderations Test (add vs int) für total_kcal
# ============================================================

mod_tests_total <- tibble(
  moderator = c("srs", "mri", "sses", "cerq_adapt", "cerq_mal", "stadit", "edeq"),
  p_int = c(
    srs_res$anova$`Pr(>Chisq)`[2],
    mri_res$anova$`Pr(>Chisq)`[2],
    sses_res$anova$`Pr(>Chisq)`[2],
    cerq_adapt_res$anova$`Pr(>Chisq)`[2],
    cerq_mal_res$anova$`Pr(>Chisq)`[2],
    stadit_res$anova$`Pr(>Chisq)`[2],
    edeq_res$anova$`Pr(>Chisq)`[2]
  )
)

mod_tests_total |>
  mutate(
    p_int = sprintf("%.3f", p_int)
  ) |>
  flextable() |>
  theme_booktabs() |>
  autofit()

```

# Sensitivity analyses

## Mismatch check

```{r}
# ============================================================
# Sensitivität: mismatch Flag im finalen Hauptsample
# ============================================================

dat_main2 <- dat_main_final |>
  select(-any_of("measured_condition")) |>
  left_join(
    condition_check |>
      select(fastress_id, session, measured_condition),
    by = c("fastress_id", "session")
  ) |>
  mutate(
    mismatch = !is.na(measured_condition) &
               !is.na(planned_condition) &
               measured_condition != planned_condition
  )

## QC
dat_main2 |>
  summarise(
    n_rows = n(),
    n_ids = n_distinct(fastress_id),
    n_missing_order = sum(is.na(order_group))
  )

# Sensitivität Sample: ohne mismatch Sessions
dat_main_nomismatch <- dat_main2 |>
  filter(mismatch == FALSE | is.na(mismatch)) |>
  group_by(fastress_id) |>
  filter(
    n_distinct(session) == 2,
    n_distinct(planned_condition) == 2
  ) |>
  ungroup()

# QC: prüfen, ob das nomismatch-Sample weiterhin ein vollständiges within-subject Sample ist
dat_main_nomismatch |>
  group_by(fastress_id) |>
  summarise(
    n_rows = n(),
    n_sessions = n_distinct(session),
    n_conditions = n_distinct(planned_condition),
    .groups = "drop"
  ) |>
  count(n_rows, n_sessions, n_conditions)

# Vergleich Basismodell total_kcal
mods_a <- fit_main_effect(dat = dat_main2, outcome = "total_kcal", use_random_slope = use_random_slope)
mods_b <- fit_main_effect(dat = dat_main_nomismatch, outcome = "total_kcal", use_random_slope = use_random_slope)

cat("\nMit allen Sessions:\n")
print(model_summary_pack(mods_a$m0, mods_a$m1, dat_main2, "total_kcal")$fixed)

cat("\nOhne mismatch Sessions:\n")
print(model_summary_pack(mods_b$m0, mods_b$m1, dat_main_nomismatch, "total_kcal")$fixed)

confint(mods_b$m1, method = "Wald")

```

Excluding sessions with metabolic mismatches did not materially change the main result.

## Log transform

```{r}
# ============================================================
# Sensitivitaet: log1p Transformation
# ============================================================

dat_main_log <- dat_main_final |>
  mutate(total_kcal_log1p = log1p(total_kcal))

mods_log <- fit_main_effect(dat = dat_main_log, outcome = "total_kcal_log1p", use_random_slope = use_random_slope)
pack_log <- model_summary_pack(mods_log$m0, mods_log$m1, dat_main_log, "total_kcal_log1p")

pack_log$comparison
pack_log$fixed
pack_log$ci

```

The null effect remained unchanged when total caloric intake was log-transformed, indicating that the main finding was not driven by skewness of the outcome distribution.

## Outlier check

### Sample trimming rule

Extreme observations were defined as sessions above the 99th percentile of total caloric intake.

```{r}
# ============================================================
# Sensitivität: Ausreisser nach 99 Prozent Quantil
# ============================================================

q99 <- dat_main_final |>
  summarise(q99 = quantile(total_kcal, 0.99, na.rm = TRUE)) |>
  pull(q99)

dat_main_trim <- dat_main_final |>
  mutate(is_outlier99 = total_kcal > q99)

dat_main_no_out <- dat_main_trim |>
  filter(is_outlier99 == FALSE)

mods_full <- fit_main_effect(dat = dat_main_trim, outcome = "total_kcal", use_random_slope = use_random_slope)
mods_trim <- fit_main_effect(dat = dat_main_no_out, outcome = "total_kcal", use_random_slope = use_random_slope)


```

### Primary model including all observations

```{r}

model_summary_pack(mods_full$m0, mods_full$m1, dat_main_trim, "total_kcal")$fixed |>
  as.data.frame() |>
  flextable()

confint(mods_trim$m1, method = "Wald")

```

### Primary model after excluding extreme observations

```{r}
model_summary_pack(mods_trim$m0, mods_trim$m1, dat_main_no_out, "total_kcal")$fixed |>
  as.data.frame() |>
  flextable()

```

# Plots and diagnostics

## Plots

### Main outcome plot (total_kcal)

```{r}
# ============================================================
# Figure: Main outcome plot (total_kcal)
# ============================================================

sum_total <- mean_ci_tbl(dat_main_final, "total_kcal")

p_total_main <- ggplot(
  dat_main_final,
  aes(x = planned_condition, y = total_kcal, group = fastress_id)
) +
  geom_line(alpha = 0.35) +
  geom_point(size = 2, alpha = 0.7) +
  geom_line(
    data = sum_total,
    aes(x = planned_condition, y = mean, group = 1),
    linewidth = 1.1,
    inherit.aes = FALSE
  ) +
  geom_point(
    data = sum_total,
    aes(x = planned_condition, y = mean),
    size = 3.5,
    inherit.aes = FALSE
  ) +
  geom_errorbar(
    data = sum_total,
    aes(x = planned_condition, ymin = ci_low, ymax = ci_high),
    width = 0.08,
    linewidth = 0.8,
    inherit.aes = FALSE
  ) +
  scale_x_discrete(labels = cond_labels) +
  labs(
    title = "Total caloric intake by metabolic condition",
    x = "Metabolic condition",
    y = "Total kcal consumed"
  ) +
  plot_theme

p_total_main

```

### Secondary outcomes by condition

```{r}
# ============================================================
# Figure: Secondary outcomes by condition
# ============================================================

secondary_long <- dat_main_final |>
  select(
    fastress_id, planned_condition,
    total_kcal, high_kcal, low_kcal, prop_high_kcal
  ) |>
  pivot_longer(
    cols = c(total_kcal, high_kcal, low_kcal, prop_high_kcal),
    names_to = "outcome",
    values_to = "value"
  ) |>
  mutate(
    outcome = factor(
      outcome,
      levels = c("total_kcal", "high_kcal", "low_kcal", "prop_high_kcal"),
      labels = c("Total kcal", "High-kcal foods", "Low-kcal foods", "Proportion high-kcal")
    )
  )

secondary_sum <- secondary_long |>
  group_by(outcome, planned_condition) |>
  summarise(
    mean = mean(value, na.rm = TRUE),
    sd = sd(value, na.rm = TRUE),
    n = sum(!is.na(value)),
    se = sd / sqrt(n),
    ci_low = mean - 1.96 * se,
    ci_high = mean + 1.96 * se,
    .groups = "drop"
  )

p_secondary <- ggplot(
  secondary_sum,
  aes(x = planned_condition, y = mean, group = 1)
) +
  geom_line(linewidth = 1) +
  geom_point(size = 3) +
  geom_errorbar(aes(ymin = ci_low, ymax = ci_high), width = 0.08) +
  facet_wrap(~ outcome, scales = "free_y") +
  scale_x_discrete(labels = cond_labels) +
  labs(
    title = "Outcomes by metabolic condition",
    x = "Metabolic condition",
    y = "Mean outcome"
  ) +
  plot_theme

p_secondary
```

### Example interaction plot for SRS

```{r}
# ============================================================
# Figure: SRS interaction at three levels
# ============================================================

srs_sd <- sd(dat_main_srs$srs_c, na.rm = TRUE)

pred_srs <- expand.grid(
  planned_condition = levels(dat_main_srs$planned_condition),
  srs_c = c(-srs_sd, 0, srs_sd)
) |>
  as_tibble() |>
  mutate(
    srs_level = factor(
      srs_c,
      levels = c(-srs_sd, 0, srs_sd),
      labels = c("Low SRS (-1 SD)", "Mean SRS", "High SRS (+1 SD)")
    )
  )

pred_srs$pred <- predict(srs_res$int, newdata = pred_srs, re.form = NA)

p_srs_interaction <- ggplot(
  pred_srs,
  aes(x = planned_condition, y = pred, group = srs_level, linetype = srs_level)
) +
  geom_line(linewidth = 1) +
  geom_point(size = 2.5) +
  scale_x_discrete(labels = cond_labels) +
  labs(
    title = "Predicted total caloric intake by condition and SRS",
    x = "Metabolic condition",
    y = "Predicted total kcal",
    linetype = "SRS level"
  ) +
  plot_theme

p_srs_interaction
```

## Diagnostics

### Residual diagnostics

```{r}
# ============================================================
# Modellannahmen und Diagnostics für total_kcal (Hauptmodell)
# ============================================================

m_total <- results_main[["total_kcal"]]$m1

# Residuen vs Fits
plot(m_total, which = 1)

# QQ Plot der Residuen
qqnorm(resid(m_total))
qqline(resid(m_total))


```

### Sessions with the largest residuals

```{r}

diag_df <- dat_main_final |>
  mutate(
    fitted = fitted(m_total),
    resid = resid(m_total),
    resid_z = as.numeric(scale(resid))
  ) |>
  arrange(desc(abs(resid_z)))

diag_df |>
  select(fastress_id, session, planned_condition, total_kcal, fitted, resid, resid_z) |>
  slice_head(n = 10)

```

## Primary model

```{r}
# ============================================================
# Basismodell report ready (total_kcal)
# ============================================================

# Nullmodell (nur Random Intercept)
m0_total <- results_main[["total_kcal"]]$m0

# Modellvergleich (Likelihood Ratio Test)
m1_total <- results_main[["total_kcal"]]$m1


```

### Model comparison

```{r}

anova(m0_total, m1_total)

```

### Confidence intervals

```{r}
# Prozent CI für Fixed Effects
confint(m1_total, method = "Wald")


```

### Fixed effects of the primary model

```{r}
# Fixed Effects Tabelle kompakt
summary(m1_total)

model_fixed_table(m1_total)

```

### Standardised effect size

```{r}

# Effektgrösse: Condition Effekt in SD Einheiten (bezogen auf dat_main)
sd_total <- dat_main_final |>
  summarise(sd_total = sd(total_kcal, na.rm = TRUE)) |>
  pull(sd_total)

beta_cond <- fixef(m1_total)[grep("^planned_condition", names(fixef(m1_total)))][1]
beta_cond / sd_total

```

# Individual Examples plot

```{r}
# ============================================================
# Individual examples plot
# ============================================================

example_ids <- c("sub-001", "sub-039", "sub-004")

example_labels <- c(
  "sub-001" = "Participant A",
  "sub-039" = "Participant B", 
  "sub-004" = "Participant C"
)

p_individual <- dat_main_final |>
  filter(fastress_id %in% example_ids) |>
  mutate(
    participant = recode(fastress_id, !!!example_labels),
    planned_condition = factor(
      planned_condition, 
      levels = c("satiated", "fasted"),
      labels = c("Satiated", "Fasted")
    )
  ) |>
  ggplot(aes(x = planned_condition, y = total_kcal, fill = planned_condition)) +
  geom_col(width = 0.6) +
  geom_text(
    aes(label = round(total_kcal, 0)),
    vjust = -0.5,
    size = 5
  ) +
  facet_wrap(~participant) +
  scale_fill_manual(values = c("Satiated" = "grey70", "Fasted" = "grey30")) +
  scale_y_continuous(expand = expansion(mult = c(0, 0.15))) +
  labs(
    x = "Metabolic condition",
    y = "Total kcal consumed",
    title = "Individual examples of intake patterns"
  ) +
  theme_classic(base_size = 16) +
  theme(legend.position = "none")

p_individual

# Spaghetti Plot
p_individual_2 <- dat_main_final |>
  filter(fastress_id %in% example_ids) |>
  mutate(
    participant = recode(fastress_id, !!!example_labels),
    planned_condition = factor(
      planned_condition,
      levels = c("satiated", "fasted"),
      labels = c("Satiated", "Fasted")
    )
  ) |>
  ggplot(aes(x = planned_condition, y = total_kcal, group = participant)) +
  geom_line(linewidth = 1.2) +
  geom_point(size = 4) +
  geom_text(
    aes(label = round(total_kcal, 0)),
    vjust = -1.5,
    size = 5
  ) +
  facet_wrap(~participant) +
  scale_y_continuous(expand = expansion(mult = c(0.1, 0.2))) +
  labs(
    x = "Metabolic condition",
    y = "Total kcal consumed",
    title = "Individual examples of intake patterns"
  ) +
  theme_classic(base_size = 16)

p_individual_2
```

# Export

## Save final outputs

```{r}
# ============================================================
# Export figures
# ============================================================

dir.create("figures", showWarnings = FALSE)

# Manipulation checks
ggsave(
  filename = "figures/figure_stress_check.png",
  plot = p_stress_check,
  width = 7, height = 5, dpi = 300, bg = "white"
)

ggsave(
  filename = "figures/figure_manip_checks.png",
  plot = p_manip_checks,
  width = 9, height = 6, dpi = 300, bg = "white"
)

# Main outcome
ggsave(
  filename = "figures/figure_total_main.png",
  plot = p_total_main,
  width = 7, height = 5, dpi = 300, bg = "white"
)

# Forest plot
ggsave(
  filename = "figures/figure_forest_main.png",
  plot = p_forest_main,
  width = 8, height = 5, dpi = 300, bg = "white"
)

# Secondary outcomes
ggsave(
  filename = "figures/figure_secondary_outcomes.png",
  plot = p_secondary,
  width = 9, height = 7, dpi = 300, bg = "white"
)

# SRS interaction
ggsave(
  filename = "figures/figure_srs_interaction.png",
  plot = p_srs_interaction,
  width = 7, height = 5, dpi = 300, bg = "white"
)

# Individual examples
ggsave(
  filename = "figures/figure_individual_examples.png",
  plot = p_individual,
  width = 9, height = 5, dpi = 300, bg = "white"
)

ggsave(
  filename = "figures/figure_individual_examples_2.png",
  plot = p_individual_2,
  width = 9, height = 5, dpi = 300, bg = "white"
)
```

# Package References

```{r}

report::cite_packages(sessionInfo())
```
